Syntax and Semantics of Abstract Binding Trees

### 2015-11-24 paper.tex
Define calculation of free variables

@@

Abts are identified up to $\alpha$-equivalence. Let $\FV{M}$ be the collection
of variables free in $M$, which is easily calculated by recursion on the
structure of $M$. We also intend to calculate the collection $\FS{M}$ of
symbols free in $M$, but this is more involved.

\subsection{Renaming of Symbols}

@@

\subsection{Substitution of Variables}

@@

\subsection{Substitution of Metavariables}

>>>>

\newcommand\CalcFV[2]{
  \FV{\IMode{#1}}\leadsto \OMode{#2}
}

@@

Abts are identified up to $\alpha$-equivalence.

\subsection{Calculating free variables}

Let $\FV{M}$ be the collection of variables free in $M$, which is easily
calculated by recursion on the structure of $M$, as follows:

\begin{gather*}
  \infer[\textit{var}]{
    \CalcFV{x}{\MkSet{x}}
  }{
  }\\[6pt]
  %
  \infer[\textit{mvar}]{
    \CalcFV{
      \MApp{\MV{m}}{\vec{u}}{M_0,\dots,M_n}
    }{
      \bigcup_{i\leq n} \vec{x}_i
    }
  }{
    \HypJ{
      \CalcFV{M_i}{\vec{x}_i}
    }{
      \Leq{i}{n}
    }
  }\\[6pt]
  %
  \infer[\textit{app}]{
    \CalcFV{
      \App{\vartheta}{E_0,\dots,E_n}
    }{
      \bigcup_{i\leq n} \vec{x}_i
    }
  }{
    \HypJ{
      \CalcFV{E_i}{\vec{x}_i}
    }{
      \Leq{i}{n}
    }
  }\\[6pt]
  %
  \infer[\textit{abs}]{
    \CalcFV{
      \MkBTm{\vec{u}}{\vec{y}}{M}
    }{
      \vec{x}\setminus\vec{y}
    }
  }{
    \CalcFV{M}{\vec{x}}
  }
\end{gather*}

Because this is a total relation, henceforth we will write $\FV{M}$ for
$\vec{x}$ when $\CalcFV{M}{x}$.

\subsection{Renaming of symbols}

@@

\subsection{Substitution of variables}

@@

\subsection{Substitution of metavariables}
